|

### 2020-05-18 paper/Manuscript.Rmd
Another update

The TOP-guidelines are primarily geared towards top-down systemic change by journals, funders, and organizations.
However, large organizations are slow to change.
For example, a snapshot of editorial practices indicated that, in 2015, only 3% out of 1151 psychology journals explicitly stated that they accepted replication studies [@martinArePsychologyJournals2017; see also @klebelPeerReviewPreprint2020].
<!-- A more recent preprint reported that many journals do not explicitly state their policies about  klebelPeerReviewPreprint2020 -->
At the same time, there is substantial momentum for grassroots change [@nosekScientificUtopiaOpening2012].
Many individual researchers are willing to adopt best practices for open science, even in the absence of institutional support.
The formation of "Open Science Communities" at universities around the globe illustrates this grassroots movement.
This paper is designed as an instrument for grassroots change, that can help individual scientists to meet the principles of open science.
This workflow can be used regardless of any top-down open science requirements already implemented by journals and institutions, and where such requirements do exist, this workflow will help fulfill them.

@@

## Prerequisites
<!--Barbara: I'm moving up this section and editing it a bit, to introduce more explicitly that worcs was developed for R.-->
WORCS has focused on developing a workflow for R, instead of for SPSS or Python.
<!-- Barbara: same as for Git, I could not find a citation. Maybe cite the website: www.r-project.org -->
Several arguments support the choice to work in R.
First, R and all of it extensions are free and Open Source, and Open Source software should be the tool of choice for open science.
Second, many tools for an open science workflow are already implemented in R.
A vibrant online community exists for R, developing new R methods and packages, and providing support and tutorials for existing ones.
Wrappers in R are often available for tools developed in other programming languages.
<!-- LB: Perhaps give some pointers to learn R (e.g. R4DataScience)-->
Third, at the time of writing, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper.
Finally, R is highly interoperable:
Packages are available to load nearly every imaginable filetype, code written in other programming languages [including Python, @allaireMarkdownPythonEngine] can be called from R, and output can be written to many file types, including DOCX and PDF (in APA style), and HTML format.

@@

  @Manual{,
    title = {RStudio: Integrated Development Environment for R},
    author = {{RStudio Team}},
    organization = {RStudio, Inc.},
    address = {Boston, MA},
    year = {2016},
    url = {http://www.rstudio.com/},
  }
-->
Many of the tools used in WORCS are embedded directly into the user interface of RStudio.
RStudio automates and streamlines many tedious or complicated aspects of working with R, Rmarkdown, and Git/GitHub.
This makes RStudio a comprehensive solution for open science research projects.
Another important feature of RStudio is project management.
A project bundles writing, analyses, data, references, etcetera, into a self-contained folder, that can be uploaded entirely to GitHub and downloaded by future users.
The `worcs` R-package installs a new RStudio project template.
When a new project is initialized from this template, much of the bookkeeping required to set up an open science project is performed automatically.

>>>>

The TOP-guidelines are primarily geared towards top-down systemic change by journals, funders, and organizations.
However, large organizations are slow to change.
For example, a snapshot of editorial practices indicated that, in 2015, only 3% out of 1151 psychology journals explicitly stated that they accepted replication studies [@martinArePsychologyJournals2017; see also @klebelPeerReviewPreprint2020].
At the same time, there is substantial momentum for grassroots change [@nosekScientificUtopiaOpening2012].
Many individual researchers are willing to adopt best practices for open science, even in the absence of institutional support.
The formation of "Open Science Communities" at universities around the globe illustrates this grassroots movement.
This paper is designed as an instrument for grassroots change, that can help individual scientists to meet the principles of open science.
This workflow can be used regardless of any top-down open science requirements already implemented by journals and institutions, and where such requirements do exist, this workflow will help fulfill them.

@@

## Prerequisites

Although the principles underlying this workflow are universal, WORCS has been optimized for R [@rcoreteamLanguageEnvironmentStatistical2020].
Several arguments support the choice to work in R.
First, R and all of it extensions are free and Open Source, and Open Source software should be the tool of choice for open science.
Second, as of this writing, R is the most advanced programming language in terms of the implementation of tools required for an open science workflow.
Third, R is well-supported; a vibrant online community exists for R, developing new R methods and packages, and providing support and tutorials for existing ones.

<!-- LB: Perhaps give some pointers to learn R (e.g. R4DataScience)-->
Third, at the time of writing, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper.
Finally, R is highly interoperable:
Packages are available to load nearly every imaginable filetype, and output can be written to most file types, including DOCX and PDF (in APA style), and HTML format. 
Moreover, wrappers are available for many tools developed in other programming languages, and code written in other programming languages can be evaluated from R [including C++, Fortran, and Python, @allaireMarkdownPythonEngine].

@@

  @Manual{,
    title = {RStudio: Integrated Development Environment for R},
    author = {{RStudio Team}},
    organization = {RStudio, Inc.},
    address = {Boston, MA},
    year = {2016},
    url = {http://www.rstudio.com/},
  }
-->
Most of the tools used in WORCS are embedded directly into the user interface of RStudio.
RStudio automates and streamlines tedious or complicated aspects of working with R, Rmarkdown, and Git/GitHub.
This makes RStudio a comprehensive solution for open science research projects.
Another important feature of RStudio is project management.
A project bundles writing, analyses, data, references, etcetera, into a self-contained folder, that can be uploaded entirely to GitHub and downloaded by future users.
The `worcs` R-package installs a new RStudio project template.
When a new project is initialized from this template, the bookkeeping required to set up an open science project is performed automatically.
